---
title: "Slendr Simulations Europe"
author: "Jose Antonio Urban Aragon"
date: "3/4/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Define broader geographic regions
```{r}
map <- world(
  xrange = c(-15, 60), # min-max longitude
  yrange = c(20, 65),  # min-max latitude
  crs = "EPSG:3035"    # projected CRS used internally
)

plot_map(map)

africa <- region(
  "Africa", map,
  polygon = list(c(-18, 20), c(40, 20), c(30, 33),
                 c(20, 32), c(10, 35), c(-8, 35))
)
europe <- region(
  "Europe", map,
  polygon = list(
    c(-8, 35), c(-5, 36), c(10, 38), c(20, 35), c(25, 35),
    c(33, 45), c(20, 58), c(-5, 60), c(-15, 50)
  )
)
anatolia <- region(
  "Anatolia", map,
  polygon = list(c(28, 35), c(40, 35), c(42, 40),
                 c(30, 43), c(27, 40), c(25, 38))
)
```


## Define demographic history and population boundaries
```{r}
afr <- population( # African ancestral population
  "AFR", parent = "ancestor", time = 52000, N = 3000,
  map = map, polygon = africa
)

ooa <- population( # population of the first migrants out of Africa
  "OOA", parent = afr, time = 51000, N = 500, remove = 25000,
  center = c(33, 30), radius = 400e3
) %>%
  move(
    trajectory = list(c(40, 30), c(50, 30), c(60, 40)),
    start = 50000, end = 40000, snapshots = 20
  )

ehg <- population( # Eastern hunter-gatherers
  "EHG", parent = ooa, time = 28000, N = 1000, remove = 6000,
  polygon = list(
    c(26, 55), c(38, 53), c(48, 53), c(60, 53),
    c(60, 60), c(48, 63), c(38, 63), c(26, 60))
)

eur <- population( # European population
  name = "EUR", parent = ehg, time = 25000, N = 2000,
  polygon = europe
)

ana <- population( # Anatolian farmers
  name = "ANA", time = 28000, N = 3000, parent = ooa, remove = 4000,
  center = c(34, 38), radius = 500e3, polygon = anatolia
) %>%
  expand_range( # expand the range by 2.500 km
    by = 2500e3, start = 10000, end = 7000,
    polygon = join(europe, anatolia), snapshots = 20
  )

yam <- population( # Yamnaya steppe population
  name = "YAM", time = 7000, N = 500, parent = ehg, remove = 2500,
  polygon = list(c(26, 50), c(38, 49), c(48, 50),
                 c(48, 56), c(38, 59), c(26, 56))
) %>%  move(trajectory = list(c(15, 50)), start = 5000, end = 3000, snapshots = 10)

```


## Define geneflow events
```{r}
gf <- list(
  gene_flow(from = ana, to = yam, rate = 0.5, start = 6500, end = 6400, overlap = FALSE),
  gene_flow(from = ana, to = eur, rate = 0.5, start = 8000, end = 6000),
  gene_flow(from = yam, to = eur, rate = 0.75, start = 4000, end = 3000)
)
```

## Compile the model to a set of configuration files

```{r}
model <- compile_model(
  populations = list(afr, ooa, ehg, eur, ana, yam), # populations defined above
  geneflow = gf, # geneflow events defined above
  generation_time = 30,
  resolution = 10e3, # resolution in meters per pixel
  competition_dist = 130e3, mate_dist = 100e3, # spatial interaction in SLiM
  dispersal_dist = 70e3, # how far will offspring end up from their parents
  path = NULL
)
```


## Schedule populations sampling 
We will sample 10 individuals from different locations accross Europe. 
```{r}

samples <- dplyr::bind_rows(
  schedule_sampling(model, times = c(12000,5000,2000), locations = list(c(15,50)), list(eur, 10)),
  schedule_sampling(model, times = c(12000,5000,2000), locations = list(c(16,55)), list(eur, 10)),
  schedule_sampling(model, times = c(12000,5000,2000), locations = list(c(17,60)), list(eur, 10)),
  schedule_sampling(model, times = c(12000,5000,2000), locations = list(c(18,65)), list(eur, 10)),
  schedule_sampling(model, times = c(12000,5000,2000), locations = list(c(19,62)), list(eur, 10)),
  schedule_sampling(model, times = c(12000,5000,2000), locations = list(c(20,61)), list(eur, 10)),
)
#test_eur <- schedule_sampling(model, times = c(12000,5000,2000), locations = list(c(15,50)), list(eur, 10))


```


# Test slim run

```{r}
slim(
  model, sequence_length = 100e3, recombination_rate = 1e-8, burnin = 200e3,
  sampling = samples, method = "batch", random_seed = 314159, max_attempts = 1
)
```

## Test ts load

```{r}
ts <- ts_load(model, recapitate = TRUE, simplify = TRUE, recombination_rate = 1e-8, Ne = 10000, random_seed = 314159)

```


## Test ts load

```{r}
data <- ts_data(ts)
```

## Plotting locations of simulated sampled individuals


```{r}
sampled_data <- ts_data(ts) %>% filter(remembered)

ggplot() +
  geom_sf(data = map, fill = "lightgray", color = NA) +
  geom_sf(data = sampled_data, aes(shape = pop, color = time)) +
  ggtitle("Locations of simulated sampled individuals") +
  scale_color_continuous(type = "viridis") +
  theme_bw()

```


